---
title: "Figure 3 (a)"
output: html_notebook
---

This script will generate Figure 3 (a) of our manuscript, alongside all statistical data we have reported in our text.

Load the necessary R libraries.

```{r}
library(plyr)
library(dplyr)
library(stringr)
library(dunn.test)
```

Load the CSV files into a dataframe.

```{r}
df_forwarding <- read.csv(file = "../../run/output/marenostrum-4/results/results.csv", sep = ";")
df_gpfs <- read.csv(file = "../../run/output/marenostrum-4-gpfs/results/results.csv", sep = ";")

df <- rbind(df_forwarding, df_gpfs)

str(df)
```

Compute the Dunn test for all I/O forwarding choices in each scenario.

```{r}
df_full <- df

df_full$layout_name <- revalue(as.factor(df_full$layout), c(
    "0" = 'file-per-process',
    "1" = 'shared-file'
))

df_full$spatiality_name <- revalue(as.factor(df_full$spatiality), c(
    "0" = 'contiguous',
    "1" = 'strided'
))


df_full$scenario <- paste(sep = '-', df_full$processes, df_full$clients, df_full$layout, df_full$spatiality, df_full$request, df_full$odirect)

results <- data.frame(
  'scenario' = factor(),
  'comparison '= factor(),
  'p.value' = double()
)

results_choices <- data.frame(
  'scenario' = factor(),
  'options' = list()
)

for (scenario in unique(df_full$scenario)) {
   data <- df_full[df_full$scenario == scenario, ]

   fwd_0 <- data[data$forwarders == 0, ]$bandwidth
   fwd_1 <- data[data$forwarders == 1, ]$bandwidth
   fwd_2 <- data[data$forwarders == 2, ]$bandwidth
   fwd_4 <- data[data$forwarders == 4, ]$bandwidth
   fwd_8 <- data[data$forwarders == 8, ]$bandwidth

   dunn_result <- dunn.test(list(fwd_0, fwd_1, fwd_2, fwd_4, fwd_8))

   tmp <- data.frame(
     dunn_result$comparisons,
     dunn_result$Z
   )

   names(tmp) <- c('comparison', 'p')

   tmp$comparison <- revalue(
     tmp$comparison,
     c(
       '1 - 2' = '0 vs. 1',
       '1 - 3' = '0 vs. 2',
       '1 - 4' = '0 vs. 4',
       '1 - 5' = '0 vs. 8',
       '2 - 3' = '1 vs. 2',
       '2 - 4' = '1 vs. 4',
       '2 - 5' = '1 vs. 8',
       '3 - 4' = '2 vs. 4',
       '3 - 5' = '2 vs. 8',
       '4 - 5' = '4 vs. 8'
     )
   )
   
   # Dunn H0 is that the samples come from populations that follow the same distribution
   # We reject H0 when p <= alpha, i.e., if p > alpha we could (forced definition) say that "they come from similar distributions" (NOTICE: this is not exactly the TRUTH)

   results <<- rbind( # we need the two << to access the variable that is out of the scope
     results, 
     data.frame(
       'scenario' = as.factor(scenario),
       'comparison' = as.factor(tmp$comparison),
       'p.value' = tmp$p
     )
   )

   options <- c(0, 1, 2, 4, 8)

   for (option in sort(tmp[tmp$p > 0.05, ]$comparison, decreasing = TRUE)) {
     pair <- option %>% str_match_all("[0-9]+") %>% unlist %>% as.numeric
     
     options[options == pair[2]] <- pair[1]
   }

   results_choices <<- rbind(
     results_choices,
     data.frame(
       'scenario' = as.factor(scenario),
       'options' = paste(unlist(unique(options)), collapse = ', ')
     )
   )
}
```

What the the choices we have for each scenario that changing the number of I/O nodes would yield different performance (bandwidth)?

```{r}
data.frame(count(results_choices, options))
```

Let's group this dataframe by the number of options, thus 0, 1, 2 and 0, 1, 4 both count as 3 options:

```{r}
results_choices$count <- sapply(str_split(results_choices$options, ','), length)

str(results_choices)

results_choices$count
```

Prepare the data for Figure 3 (a).

```{r}
df_plot_options <- data.frame(count(results_choices, count))

df_plot_options$n <- as.numeric(as.character(df_plot_options$n))

df_plot_options <- df_plot_options[order(df_plot_options$n), ]
```

Generate Figure 3 (a).

```{r}
library(ggplot2)

plot <- ggplot(df_plot_options,
    aes(
        x = count,
        y = n,
        label = n
    )) +
    geom_bar(stat = "identity", fill = "#255D83") +
    geom_text(nudge_y = 5, size = 3.5) +
    expand_limits(y = 90) +
    xlab("Number of choices") + 
    ylab("Number of patterns") +
    theme_bw() +
    theme(
        legend.position = "top",
        plot.title = element_text(size = 10),
        axis.title = element_text(size = 10), 
        strip.background = element_rect(colour = NA, fill = NA)
    )

pdf(file="../output/figure-3-a.pdf", width = 2, height = 2)
plot
dev.off()

```


