---
title: "Figure 3 (b)"
output: html_notebook
---

This script will generate Figure 3 (b) of our manuscript, alongside all statistical data we have reported in our text.

Load the necessary R libraries.

```{r}
library(plyr)
library(dplyr)
library(stringr)
```

Load the CSV files into a dataframe.

```{r}
df_forwarding <- read.csv(file = "../../run/output/marenostrum-4/results/results.csv", sep = ";")
df_gpfs <- read.csv(file = "../../run/output/marenostrum-4-gpfs/results/results.csv", sep = ";")

df <- rbind(df_forwarding, df_gpfs)

str(df)
```

Get the number of I/O nodes that achieved the highest bandwidth for each scenario.

```{r}
aux <- as.data.frame(
  df_full %>%
  group_by(scenario) %>%
  slice(which.max(bandwidth))
)

aux <- subset(aux, select = c(scenario, forwarders, bandwidth))
aux
```

Count the number of scenarios (access patterns) grouped by the best number of I/O forwarding nodes for each one.

```{r}
best_choices <- data.frame(count(aux, forwarders))
best_choices
```

Generate Figure 3 (b).

```{r}
library(ggplot2)

plot <- ggplot(best_choices,
    aes(
        x = as.factor(forwarders),
        y = n,
        label = n
    )) +
    #scale_y_continuous(breaks = seq(0, 65, 5)) +
    geom_bar(stat = "identity", fill = "#255D83") +
    geom_text(nudge_y = 5, size = 3.5) +
    expand_limits(y = 90) +
    xlab("Number of I/O nodes") + 
    ylab("Number of patterns") +
    theme_bw() +
    theme(
        legend.position = "top",
        plot.title = element_text(size = 10),
        axis.title = element_text(size = 10), 
        strip.background = element_rect(colour = NA, fill = NA)
    )

pdf(file="../output/figure-3-b.pdf", width = 2, height = 2)
plot
dev.off()

```


